What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex

@@

Mei et al.~\cite{Mei2007} use context information to automatically name topics. They describe probabilistic labeling, using the frequency distribution of words in a topic to create a meaningful phrase. They do not use external domain-specific information as we do.

Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.

>>>>

% Part of our effort with this project is to understand the qualitative and intentional aspects of requirements in software evolution, a notion we first discussed in \cite{ernst07icsm}. That idea is derived from, in part, work on narratives of software systems shown in academic work like \cite{anton01}, or more general-purpose works like \cite{waldo93}.

@@

Mei et al.~\cite{Mei2007} use context information to automatically name topics. They describe probabilistic labeling, using the frequency distribution of words in a topic to create a meaningful phrase. They do not use external domain-specific information as we do.
In \cite{ernst10refsq}, we describe an application similar to this to identify change in quality requirements in GNOME software projects; our approach is solely text-matching, however, and does not leverage machine learning strategies.

% comment out or not
Massey~\cite{massey02icse} and Scacchi~\cite{scacchi02,scacchi05b} looked at the topic of requirements in open-source software. Their work discusses the source of the requirements and how they are used in the development process. German~\cite{german03gnome} looked at GNOME specifically, and listed several sources for requirements: leader interest, mimicry, brainstorming, and prototypes. None of this work  addressed quality requirements in OSS, nor did it examine requirements trends.

% Hindle et al. \cite{Hindle2007} examined release patterns in OSS. They showed that there is a difference between projects regarding maintenance techniques. This supports our result that software qualities are not discussed with the same frequency across projects.
